A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-17 tex/body.tex
more

\newcommand\gandl{G\&L}
\newcommand\HD[1]{\hbox to2.5em{\hfill#1\hfill}}

@@

@@

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}c@{\kern.5em}c@{\kern.5em}c@{\kern1.3em}c@{\;}}
  & \HD{Distro} & \HD{AFP} & \HD{\gandl} & \relax{All}
\MIDRULE
No (co)datatypes
  & 229 & 765 & \phantom{0}61 & 1055 \\[\jot]
%Datatype simplication only
%  &  \\
Datatypes without \rn{Acyclic}
  & 235 & 770 & \phantom{0}61 & 1066 \\
Full datatypes
  & 235 & 773 & \phantom{0}61 & 1069 \\[\jot]
%Codatatype simplication only
%  &  \\
Codatatypes without \rn{Unique}
  & 230 & 794 & \phantom{0}65 & 1089 \\
Full codatatypes
  & 231 & 794 & \bfseries \phantom{0}68 & 1093 \\[\jot]
Full (co)datatypes
  & \bfseries 237 & \bfseries 802 & \bfseries \phantom{0}68 & \bfseries 1107 \\[\jot]
Total number of goals
  & 879 & 2974\phantom{0} & 317 & 4170
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

>>>>

\newcommand\gandl{G\&L}
\newcommand\HD[1]{\hbox to2.3em{\hfill\!\!\!\!#1\!\!\!\!\hfill}}

@@

%  & 879 & 2974\phantom{0} & 317 & 4170

@@

%%% TODO: Fix data

\begin{table*}[tbh!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}cc@{\kern.5em}cc@{\kern.5em}cc@{\kern1.3em}cc@{\;}}
  & \multicolumn{2}{c}{Distro} & \multicolumn{2}{c}{AFP} & \multicolumn{2}{c}{\gandl} & \multicolumn{2}{c}{All} \\
  & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4}
\MIDRULE
No (co)datatypes
  & 209 & 221 & 777 & 785 & \phantom{0}51 & \phantom{0}52 & 1037 & 1048 \\[\jot]
%Datatype simplication only
%  &  \\
Datatypes w/o \rn{Acyclic}
  & & 235 & & 770 & & \phantom{0}61 & & 1066 \\
Full datatypes
  & 213 & 227 & 791 & 786 & \phantom{0}51 & \phantom{0}52 & 1055 & 1065 \\[\jot]
%Codatatype simplication only
%  &  \\
Codatatypes w/o \rn{Unique}
  & & 230 & & 794 & & \phantom{0}65 & & 1089 \\
Full codatatypes
  & & 231 & & 794 & & \bfseries \phantom{0}68 & & 1093 \\[\jot]
Full (co)datatypes
  & & \bfseries 237 & & \bfseries 802 & & \bfseries \phantom{0}68 & & \bfseries 1107% \\[\jot]
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}
